Supplementary Material

### 2021-03-21 docs/supplementary-information/report/supplementary-information.tex
#6 polishes and prepare for submission suplementary-information

\begin{abstract}
Section 1 describes datasets and section 2 shows surface plots of 3D RQA ENTR values for 3 participants (p01, p02 and p03).
\end{abstract}

@@

The location of the dataset is shown below with the first two lines of xdatav00.dt denoting labels.
\begin{verbatim}
~/srep2020/data/dataset$ tree --si
[ 46M]  xdata_v00.dt
.
.
.
"Participant" "Activity" "Sensor" "Sample" "Time" 
"sg0zmuvGyroY" "sg1zmuvGyroY" "sg2zmuvGyroY" 
"sg0zmuvGyroZ" "sg1zmuvGyroZ" "sg2zmuvGyroZ"
...
"p01" "HN" "HS01" 1 0 
0.0110396263359954 0.00606430191548277 0.0385586376765087 
0.00467559072085554 0.00509907428630649 0.168927517477539
...
\end{verbatim}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{3D RQA ENTR values}
Location of code, data and figures for 3D RQA ENTR values is shown below 
\begin{verbatim}
## Code
$HOME/srep2020/code/rscripts/G_3Drqa
`> source(  paste( getwd(), '/C_3Drqa_plots_epsilons.R', sep=''), echo=TRUE )`

## Data
$HOME/srep2020/data/rqa$ tree -s

## Figures
$HOME/srep2020/docs/figures/rqa/src/3drqa_epsilons$ tree -s
\end{verbatim}

@@

\newpage
%---------------------------------FIGURE)-------------------------------------
\begin{figure}[ht!]
\centering
\includegraphics[scale=1.0]{figures/rqa/output/epsilons/rqa-epsilonsp01w100Horizontal}
    	\caption{
	{\bf RQA-Entr for participant 01 performing horizontal movements for a window size of 100 samples.}
		%RQA-Entr surface plots are for participant $p01$
		%for horizontal and vertical arm movements in normal
		%and faster velocity (HN, HF, VN, VF)
		%with the normalised GyroZ or GyroY axis
		%((sg0) raw-normalised (sg0zmuv),
		%(sg1) normalised-smoothed 1 and
		%(sg1) normalised-smoothed 2)
		%and with one sensor attached to the participant (HS01)
		%and other sensor attached to the robot (RS01).
	Code and data to reproduce the figure is available in \cite{srep2020}.
        }
    \label{fig-p01-H-w100}
\end{figure}
%---------------------------------(FIGURE)------------------------------------
%---------------------------------FIGURE)-------------------------------------
\begin{figure}[hb!]
\centering
\includegraphics[scale=1.0]{figures/rqa/output/epsilons/rqa-epsilonsp01w100Vertical}
    	\caption{
	{\bf RQA-Entr for participant 01 performing vertical movements for a window size of 100 samples.}
		%RQA-Entr surface plots are for participant $p01$
		%for horizontal and vertical arm movements in normal
		%and faster velocity (HN, HF, VN, VF)
		%with the normalised GyroZ or GyroY axis
		%((sg0) raw-normalised (sg0zmuv),
		%(sg1) normalised-smoothed 1 and
		%(sg1) normalised-smoothed 2)
		%and with one sensor attached to the participant (HS01)
		%and other sensor attached to the robot (RS01).
	Code and data to reproduce the figure is available in \cite{srep2020}.
        }
    \label{fig-p01-V-w100}
\end{figure}
%---------------------------------(FIGURE)------------------------------------

\newpage
%---------------------------------FIGURE)-------------------------------------
\begin{figure}[ht!]
\centering
\includegraphics{figures/rqa/output/epsilons/rqa-epsilonsp01w250Horizontal}
    	\caption{
	{\bf RQA-Entr for participant 01 performing horizontal movements for a window size of 250 samples.}
		%RQA-Entr surface plots are for participant $p01$
		%for horizontal and vertical arm movements in normal
		%and faster velocity (HN, HF, VN, VF)
		%with the normalised GyroZ or GyroY axis
		%((sg0) raw-normalised (sg0zmuv),
		%(sg1) normalised-smoothed 1 and
		%(sg1) normalised-smoothed 2)
		%and with one sensor attached to the participant (HS01)
		%and other sensor attached to the robot (RS01).
	Code and data to reproduce the figure is available in \cite{srep2020}.
        }
    \label{fig-p01-H-w250}
\end{figure}
%---------------------------------(FIGURE)------------------------------------
%---------------------------------FIGURE)-------------------------------------
\begin{figure}[hb!]
\centering
\includegraphics{figures/rqa/output/epsilons/rqa-epsilonsp01w250Vertical}
    	\caption{
	{\bf RQA-Entr for participant 01 performing vertical movements for a window size of 250 samples.}
		%RQA-Entr surface plots are for participant $p01$
		%for horizontal and vertical arm movements in normal
		%and faster velocity (HN, HF, VN, VF)
		%with the normalised GyroZ or GyroY axis
		%((sg0) raw-normalised (sg0zmuv),
		%(sg1) normalised-smoothed 1 and
		%(sg1) normalised-smoothed 2)
		%and with one sensor attached to the participant (HS01)
		%and other sensor attached to the robot (RS01).
	Code and data to reproduce the figure is available in \cite{srep2020}.
        }
    \label{fig-p01-V-w250}
\end{figure}
%---------------------------------(FIGURE)------------------------------------

\newpage
%---------------------------------FIGURE)-------------------------------------
\begin{figure}[ht!]
\centering
\includegraphics{figures/rqa/output/epsilons/rqa-epsilonsp01w500Horizontal}
    	\caption{
	{\bf RQA-Entr for participant 01 performing horizontal movements for a window size of 500 samples.}
		%RQA-Entr surface plots are for participant $p01$
		%for horizontal and vertical arm movements in normal
		%and faster velocity (HN, HF, VN, VF)
		%with the normalised GyroZ or GyroY axis
		%((sg0) raw-normalised (sg0zmuv),
		%(sg1) normalised-smoothed 1 and
		%(sg1) normalised-smoothed 2)
		%and with one sensor attached to the participant (HS01)
		%and other sensor attached to the robot (RS01).
	Code and data to reproduce the figure is available in \cite{srep2020}.
        }
    \label{fig-p01-H-w500}
\end{figure}
%---------------------------------(FIGURE)------------------------------------
%---------------------------------FIGURE)-------------------------------------
\begin{figure}[hb!]
\centering
\includegraphics{figures/rqa/output/epsilons/rqa-epsilonsp01w500Vertical}
    	\caption{
	{\bf RQA-Entr for participant 01 performing vertical movements for a window size of 500 samples.}
		%RQA-Entr surface plots are for participant $p01$
		%for horizontal and vertical arm movements in normal
		%and faster velocity (HN, HF, VN, VF)
		%with the normalised GyroZ or GyroY axis
		%((sg0) raw-normalised (sg0zmuv),
		%(sg1) normalised-smoothed 1 and
		%(sg1) normalised-smoothed 2)
		%and with one sensor attached to the participant (HS01)
		%and other sensor attached to the robot (RS01).
	Code and data to reproduce the figure is available in \cite{srep2020}.
        }
    \label{fig-p01-V-w500}
\end{figure}
%---------------------------------(FIGURE)------------------------------------

\newpage
%---------------------------------FIGURE)-------------------------------------
\begin{figure}[ht!]
\centering
\includegraphics{figures/rqa/output/epsilons/rqa-epsilonsp01w750Horizontal}
    	\caption{
	{\bf RQA-Entr for participant 01 performing horizontal movements for a window size of 750 samples.}
		%RQA-Entr surface plots are for participant $p01$
		%for horizontal and vertical arm movements in normal
		%and faster velocity (HN, HF, VN, VF)
		%with the normalised GyroZ or GyroY axis
		%((sg0) raw-normalised (sg0zmuv),
		%(sg1) normalised-smoothed 1 and
		%(sg1) normalised-smoothed 2)
		%and with one sensor attached to the participant (HS01)
		%and other sensor attached to the robot (RS01).
	Code and data to reproduce the figure is available in \cite{srep2020}.
        }
    \label{fig-p01-H-w750}
\end{figure}
%---------------------------------(FIGURE)------------------------------------
%---------------------------------FIGURE)-------------------------------------
\begin{figure}[hb!]
\centering
\includegraphics{figures/rqa/output/epsilons/rqa-epsilonsp01w750Vertical}
    	\caption{
	{\bf RQA-Entr for participant 01 performing vertical movements for a window size of 750 samples.}
		%RQA-Entr surface plots are for participant $p01$
		%for horizontal and vertical arm movements in normal
		%and faster velocity (HN, HF, VN, VF)
		%with the normalised GyroZ or GyroY axis
		%((sg0) raw-normalised (sg0zmuv),
		%(sg1) normalised-smoothed 1 and
		%(sg1) normalised-smoothed 2)
		%and with one sensor attached to the participant (HS01)
		%and other sensor attached to the robot (RS01).
	Code and data to reproduce the figure is available in \cite{srep2020}.
        }
    \label{fig-p01-V-w750}
\end{figure}
%---------------------------------(FIGURE)------------------------------------

@@

\newpage
%---------------------------------FIGURE)-------------------------------------
\begin{figure}[ht!]
\centering
\includegraphics[scale=1.0]{figures/rqa/output/epsilons/rqa-epsilonsp02w100Horizontal}
    	\caption{
	{\bf RQA-Entr for participant 02 performing horizontal movements for a window size of 100 samples.}
		%RQA-Entr surface plots are for participant $p02$
		%for horizontal and vertical arm movements in normal
		%and faster velocity (HN, HF, VN, VF)
		%with the normalised GyroZ or GyroY axis
		%((sg0) raw-normalised (sg0zmuv),
		%(sg1) normalised-smoothed 1 and
		%(sg1) normalised-smoothed 2)
		%and with one sensor attached to the participant (HS01)
		%and other sensor attached to the robot (RS01).
	Code and data to reproduce the figure is available in \cite{srep2020}.
        }
    \label{fig-p02-H-w100}
\end{figure}
%---------------------------------(FIGURE)------------------------------------
%---------------------------------FIGURE)-------------------------------------
\begin{figure}[hb!]
\centering
\includegraphics[scale=1.0]{figures/rqa/output/epsilons/rqa-epsilonsp02w100Vertical}
    	\caption{
	{\bf RQA-Entr for participant 02 performing vertical movements for a window size of 100 samples.}
		%RQA-Entr surface plots are for participant $p02$
		%for horizontal and vertical arm movements in normal
		%and faster velocity (HN, HF, VN, VF)
		%with the normalised GyroZ or GyroY axis
		%((sg0) raw-normalised (sg0zmuv),
		%(sg1) normalised-smoothed 1 and
		%(sg1) normalised-smoothed 2)
		%and with one sensor attached to the participant (HS01)
		%and other sensor attached to the robot (RS01).
	Code and data to reproduce the figure is available in \cite{srep2020}.
        }
    \label{fig-p02-V-w100}
\end{figure}
%---------------------------------(FIGURE)------------------------------------

\newpage
%---------------------------------FIGURE)-------------------------------------
\begin{figure}[ht!]
\centering
\includegraphics{figures/rqa/output/epsilons/rqa-epsilonsp02w250Horizontal}
    	\caption{
	{\bf RQA-Entr for participant 02 performing horizontal movements for a window size of 250 samples.}
		%RQA-Entr surface plots are for participant $p02$
		%for horizontal and vertical arm movements in normal
		%and faster velocity (HN, HF, VN, VF)
		%with the normalised GyroZ or GyroY axis
		%((sg0) raw-normalised (sg0zmuv),
		%(sg1) normalised-smoothed 1 and
		%(sg1) normalised-smoothed 2)
		%and with one sensor attached to the participant (HS01)
		%and other sensor attached to the robot (RS01).
	Code and data to reproduce the figure is available in \cite{srep2020}.
        }
    \label{fig-p02-H-w250}
\end{figure}
%---------------------------------(FIGURE)------------------------------------
%---------------------------------FIGURE)-------------------------------------
\begin{figure}[hb!]
\centering
\includegraphics{figures/rqa/output/epsilons/rqa-epsilonsp02w250Vertical}
    	\caption{
	{\bf RQA-Entr for participant 02 performing vertical movements for a window size of 250 samples.}
		%RQA-Entr surface plots are for participant $p02$
		%for horizontal and vertical arm movements in normal
		%and faster velocity (HN, HF, VN, VF)
		%with the normalised GyroZ or GyroY axis
		%((sg0) raw-normalised (sg0zmuv),
		%(sg1) normalised-smoothed 1 and
		%(sg1) normalised-smoothed 2)
		%and with one sensor attached to the participant (HS01)
		%and other sensor attached to the robot (RS01).
	Code and data to reproduce the figure is available in \cite{srep2020}.
        }
    \label{fig-p02-V-w250}
\end{figure}
%---------------------------------(FIGURE)------------------------------------

\newpage
%---------------------------------FIGURE)-------------------------------------
\begin{figure}[ht!]
\centering
\includegraphics{figures/rqa/output/epsilons/rqa-epsilonsp02w500Horizontal}
    	\caption{
	{\bf RQA-Entr for participant 02 performing horizontal movements for a window size of 500 samples.}
		%RQA-Entr surface plots are for participant $p02$
		%for horizontal and vertical arm movements in normal
		%and faster velocity (HN, HF, VN, VF)
		%with the normalised GyroZ or GyroY axis
		%((sg0) raw-normalised (sg0zmuv),
		%(sg1) normalised-smoothed 1 and
		%(sg1) normalised-smoothed 2)
		%and with one sensor attached to the participant (HS01)
		%and other sensor attached to the robot (RS01).
	Code and data to reproduce the figure is available in \cite{srep2020}.
        }
    \label{fig-p02-H-w500}
\end{figure}
%---------------------------------(FIGURE)------------------------------------
%---------------------------------FIGURE)-------------------------------------
\begin{figure}[hb!]
\centering
\includegraphics{figures/rqa/output/epsilons/rqa-epsilonsp02w500Vertical}
    	\caption{
	{\bf RQA-Entr for participant 02 performing vertical movements for a window size of 500 samples.}
		%RQA-Entr surface plots are for participant $p02$
		%for horizontal and vertical arm movements in normal
		%and faster velocity (HN, HF, VN, VF)
		%with the normalised GyroZ or GyroY axis
		%((sg0) raw-normalised (sg0zmuv),
		%(sg1) normalised-smoothed 1 and
		%(sg1) normalised-smoothed 2)
		%and with one sensor attached to the participant (HS01)
		%and other sensor attached to the robot (RS01).
	Code and data to reproduce the figure is available in \cite{srep2020}.
        }
    \label{fig-p02-V-w500}
\end{figure}
%---------------------------------(FIGURE)------------------------------------

\newpage
%---------------------------------FIGURE)-------------------------------------
\begin{figure}[ht!]
\centering
\includegraphics{figures/rqa/output/epsilons/rqa-epsilonsp02w750Horizontal}
    	\caption{
	{\bf RQA-Entr for participant 02 performing horizontal movements for a window size of 750 samples.}
		%RQA-Entr surface plots are for participant $p02$
		%for horizontal and vertical arm movements in normal
		%and faster velocity (HN, HF, VN, VF)
		%with the normalised GyroZ or GyroY axis
		%((sg0) raw-normalised (sg0zmuv),
		%(sg1) normalised-smoothed 1 and
		%(sg1) normalised-smoothed 2)
		%and with one sensor attached to the participant (HS01)
		%and other sensor attached to the robot (RS01).
	Code and data to reproduce the figure is available in \cite{srep2020}.
        }
    \label{fig-p02-H-w750}
\end{figure}
%---------------------------------(FIGURE)------------------------------------
%---------------------------------FIGURE)-------------------------------------
\begin{figure}[hb!]
\centering
\includegraphics{figures/rqa/output/epsilons/rqa-epsilonsp02w750Vertical}
    	\caption{
	{\bf RQA-Entr for participant 02 performing vertical movements for a window size of 750 samples.}
		%RQA-Entr surface plots are for participant $p02$
		%for horizontal and vertical arm movements in normal
		%and faster velocity (HN, HF, VN, VF)
		%with the normalised GyroZ or GyroY axis
		%((sg0) raw-normalised (sg0zmuv),
		%(sg1) normalised-smoothed 1 and
		%(sg1) normalised-smoothed 2)
		%and with one sensor attached to the participant (HS01)
		%and other sensor attached to the robot (RS01).
	Code and data to reproduce the figure is available in \cite{srep2020}.
        }
    \label{fig-p02-V-w750}
\end{figure}
%---------------------------------(FIGURE)------------------------------------

>>>>

\begin{abstract}
Report for supplementary material where section 1 describes datasets and section 2 shows surface plots of 3D RQA ENTR values for 3 participants (p01, p02 and p03).
\end{abstract}

@@

The location of the dataset is shown below with the first two lines of xdatav00.dt denoting labels.
\begin{verbatim}
~/srep2021/data/dataset$ tree --si
[ 46M]  xdata_v00.dt
.
.
.
"Participant" "Activity" "Sensor" "Sample" "Time" 
"sg0zmuvGyroY" "sg1zmuvGyroY" "sg2zmuvGyroY" 
"sg0zmuvGyroZ" "sg1zmuvGyroZ" "sg2zmuvGyroZ"
...
"p01" "HN" "HS01" 1 0 
0.0110396263359954 0.00606430191548277 0.0385586376765087 
0.00467559072085554 0.00509907428630649 0.168927517477539
...
\end{verbatim}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{3D RQA ENTR values}
Location of code, data and figures for 3D RQA ENTR values is shown below 
\begin{verbatim}
## Code
$HOME/srep2021/code/rscripts/G_3Drqa
`> source(  paste( getwd(), '/C_3Drqa_plots_epsilons.R', sep=''), echo=TRUE )`

## Data
$HOME/srep2021/data/rqa$ tree -s

## Figures
$HOME/srep2021/docs/figures/rqa/src/3drqa_epsilons$ tree -s
\end{verbatim}

@@

\newpage
%---------------------------------FIGURE)-------------------------------------
\begin{figure}[ht!]
\centering
\includegraphics[scale=1.0]{figures/rqa/output/epsilons/rqa-epsilonsp01w100Horizontal}
    	\caption{
	{\bf RQA-Entr for participant 01 performing horizontal movements for a window size of 100 samples.}
		%RQA-Entr surface plots are for participant $p01$
		%for horizontal and vertical arm movements in normal
		%and faster velocity (HN, HF, VN, VF)
		%with the normalised GyroZ or GyroY axis
		%((sg0) raw-normalised (sg0zmuv),
		%(sg1) normalised-smoothed 1 and
		%(sg1) normalised-smoothed 2)
		%and with one sensor attached to the participant (HS01)
		%and other sensor attached to the robot (RS01).
	Code and data to reproduce the figure is available in \cite{srep2021}.
        }
    \label{fig-p01-H-w100}
\end{figure}
%---------------------------------(FIGURE)------------------------------------
%---------------------------------FIGURE)-------------------------------------
\begin{figure}[hb!]
\centering
\includegraphics[scale=1.0]{figures/rqa/output/epsilons/rqa-epsilonsp01w100Vertical}
    	\caption{
	{\bf RQA-Entr for participant 01 performing vertical movements for a window size of 100 samples.}
		%RQA-Entr surface plots are for participant $p01$
		%for horizontal and vertical arm movements in normal
		%and faster velocity (HN, HF, VN, VF)
		%with the normalised GyroZ or GyroY axis
		%((sg0) raw-normalised (sg0zmuv),
		%(sg1) normalised-smoothed 1 and
		%(sg1) normalised-smoothed 2)
		%and with one sensor attached to the participant (HS01)
		%and other sensor attached to the robot (RS01).
	Code and data to reproduce the figure is available in \cite{srep2021}.
        }
    \label{fig-p01-V-w100}
\end{figure}
%---------------------------------(FIGURE)------------------------------------

\newpage
%---------------------------------FIGURE)-------------------------------------
\begin{figure}[ht!]
\centering
\includegraphics{figures/rqa/output/epsilons/rqa-epsilonsp01w250Horizontal}
    	\caption{
	{\bf RQA-Entr for participant 01 performing horizontal movements for a window size of 250 samples.}
		%RQA-Entr surface plots are for participant $p01$
		%for horizontal and vertical arm movements in normal
		%and faster velocity (HN, HF, VN, VF)
		%with the normalised GyroZ or GyroY axis
		%((sg0) raw-normalised (sg0zmuv),
		%(sg1) normalised-smoothed 1 and
		%(sg1) normalised-smoothed 2)
		%and with one sensor attached to the participant (HS01)
		%and other sensor attached to the robot (RS01).
	Code and data to reproduce the figure is available in \cite{srep2021}.
        }
    \label{fig-p01-H-w250}
\end{figure}
%---------------------------------(FIGURE)------------------------------------
%---------------------------------FIGURE)-------------------------------------
\begin{figure}[hb!]
\centering
\includegraphics{figures/rqa/output/epsilons/rqa-epsilonsp01w250Vertical}
    	\caption{
	{\bf RQA-Entr for participant 01 performing vertical movements for a window size of 250 samples.}
		%RQA-Entr surface plots are for participant $p01$
		%for horizontal and vertical arm movements in normal
		%and faster velocity (HN, HF, VN, VF)
		%with the normalised GyroZ or GyroY axis
		%((sg0) raw-normalised (sg0zmuv),
		%(sg1) normalised-smoothed 1 and
		%(sg1) normalised-smoothed 2)
		%and with one sensor attached to the participant (HS01)
		%and other sensor attached to the robot (RS01).
	Code and data to reproduce the figure is available in \cite{srep2021}.
        }
    \label{fig-p01-V-w250}
\end{figure}
%---------------------------------(FIGURE)------------------------------------

\newpage
%---------------------------------FIGURE)-------------------------------------
\begin{figure}[ht!]
\centering
\includegraphics{figures/rqa/output/epsilons/rqa-epsilonsp01w500Horizontal}
    	\caption{
	{\bf RQA-Entr for participant 01 performing horizontal movements for a window size of 500 samples.}
		%RQA-Entr surface plots are for participant $p01$
		%for horizontal and vertical arm movements in normal
		%and faster velocity (HN, HF, VN, VF)
		%with the normalised GyroZ or GyroY axis
		%((sg0) raw-normalised (sg0zmuv),
		%(sg1) normalised-smoothed 1 and
		%(sg1) normalised-smoothed 2)
		%and with one sensor attached to the participant (HS01)
		%and other sensor attached to the robot (RS01).
	Code and data to reproduce the figure is available in \cite{srep2021}.
        }
    \label{fig-p01-H-w500}
\end{figure}
%---------------------------------(FIGURE)------------------------------------
%---------------------------------FIGURE)-------------------------------------
\begin{figure}[hb!]
\centering
\includegraphics{figures/rqa/output/epsilons/rqa-epsilonsp01w500Vertical}
    	\caption{
	{\bf RQA-Entr for participant 01 performing vertical movements for a window size of 500 samples.}
		%RQA-Entr surface plots are for participant $p01$
		%for horizontal and vertical arm movements in normal
		%and faster velocity (HN, HF, VN, VF)
		%with the normalised GyroZ or GyroY axis
		%((sg0) raw-normalised (sg0zmuv),
		%(sg1) normalised-smoothed 1 and
		%(sg1) normalised-smoothed 2)
		%and with one sensor attached to the participant (HS01)
		%and other sensor attached to the robot (RS01).
	Code and data to reproduce the figure is available in \cite{srep2021}.
        }
    \label{fig-p01-V-w500}
\end{figure}
%---------------------------------(FIGURE)------------------------------------

\newpage
%---------------------------------FIGURE)-------------------------------------
\begin{figure}[ht!]
\centering
\includegraphics{figures/rqa/output/epsilons/rqa-epsilonsp01w750Horizontal}
    	\caption{
	{\bf RQA-Entr for participant 01 performing horizontal movements for a window size of 750 samples.}
		%RQA-Entr surface plots are for participant $p01$
		%for horizontal and vertical arm movements in normal
		%and faster velocity (HN, HF, VN, VF)
		%with the normalised GyroZ or GyroY axis
		%((sg0) raw-normalised (sg0zmuv),
		%(sg1) normalised-smoothed 1 and
		%(sg1) normalised-smoothed 2)
		%and with one sensor attached to the participant (HS01)
		%and other sensor attached to the robot (RS01).
	Code and data to reproduce the figure is available in \cite{srep2021}.
        }
    \label{fig-p01-H-w750}
\end{figure}
%---------------------------------(FIGURE)------------------------------------
%---------------------------------FIGURE)-------------------------------------
\begin{figure}[hb!]
\centering
\includegraphics{figures/rqa/output/epsilons/rqa-epsilonsp01w750Vertical}
    	\caption{
	{\bf RQA-Entr for participant 01 performing vertical movements for a window size of 750 samples.}
		%RQA-Entr surface plots are for participant $p01$
		%for horizontal and vertical arm movements in normal
		%and faster velocity (HN, HF, VN, VF)
		%with the normalised GyroZ or GyroY axis
		%((sg0) raw-normalised (sg0zmuv),
		%(sg1) normalised-smoothed 1 and
		%(sg1) normalised-smoothed 2)
		%and with one sensor attached to the participant (HS01)
		%and other sensor attached to the robot (RS01).
	Code and data to reproduce the figure is available in \cite{srep2021}.
        }
    \label{fig-p01-V-w750}
\end{figure}
%---------------------------------(FIGURE)------------------------------------

@@

\newpage
%---------------------------------FIGURE)-------------------------------------
\begin{figure}[ht!]
\centering
\includegraphics[scale=1.0]{figures/rqa/output/epsilons/rqa-epsilonsp02w100Horizontal}
    	\caption{
	{\bf RQA-Entr for participant 02 performing horizontal movements for a window size of 100 samples.}
		%RQA-Entr surface plots are for participant $p02$
		%for horizontal and vertical arm movements in normal
		%and faster velocity (HN, HF, VN, VF)
		%with the normalised GyroZ or GyroY axis
		%((sg0) raw-normalised (sg0zmuv),
		%(sg1) normalised-smoothed 1 and
		%(sg1) normalised-smoothed 2)
		%and with one sensor attached to the participant (HS01)
		%and other sensor attached to the robot (RS01).
	Code and data to reproduce the figure is available in \cite{srep2021}.
        }
    \label{fig-p02-H-w100}
\end{figure}
%---------------------------------(FIGURE)------------------------------------
%---------------------------------FIGURE)-------------------------------------
\begin{figure}[hb!]
\centering
\includegraphics[scale=1.0]{figures/rqa/output/epsilons/rqa-epsilonsp02w100Vertical}
    	\caption{
	{\bf RQA-Entr for participant 02 performing vertical movements for a window size of 100 samples.}
		%RQA-Entr surface plots are for participant $p02$
		%for horizontal and vertical arm movements in normal
		%and faster velocity (HN, HF, VN, VF)
		%with the normalised GyroZ or GyroY axis
		%((sg0) raw-normalised (sg0zmuv),
		%(sg1) normalised-smoothed 1 and
		%(sg1) normalised-smoothed 2)
		%and with one sensor attached to the participant (HS01)
		%and other sensor attached to the robot (RS01).
	Code and data to reproduce the figure is available in \cite{srep2021}.
        }
    \label{fig-p02-V-w100}
\end{figure}
%---------------------------------(FIGURE)------------------------------------

\newpage
%---------------------------------FIGURE)-------------------------------------
\begin{figure}[ht!]
\centering
\includegraphics{figures/rqa/output/epsilons/rqa-epsilonsp02w250Horizontal}
    	\caption{
	{\bf RQA-Entr for participant 02 performing horizontal movements for a window size of 250 samples.}
		%RQA-Entr surface plots are for participant $p02$
		%for horizontal and vertical arm movements in normal
		%and faster velocity (HN, HF, VN, VF)
		%with the normalised GyroZ or GyroY axis
		%((sg0) raw-normalised (sg0zmuv),
		%(sg1) normalised-smoothed 1 and
		%(sg1) normalised-smoothed 2)
		%and with one sensor attached to the participant (HS01)
		%and other sensor attached to the robot (RS01).
	Code and data to reproduce the figure is available in \cite{srep2021}.
        }
    \label{fig-p02-H-w250}
\end{figure}
%---------------------------------(FIGURE)------------------------------------
%---------------------------------FIGURE)-------------------------------------
\begin{figure}[hb!]
\centering
\includegraphics{figures/rqa/output/epsilons/rqa-epsilonsp02w250Vertical}
    	\caption{
	{\bf RQA-Entr for participant 02 performing vertical movements for a window size of 250 samples.}
		%RQA-Entr surface plots are for participant $p02$
		%for horizontal and vertical arm movements in normal
		%and faster velocity (HN, HF, VN, VF)
		%with the normalised GyroZ or GyroY axis
		%((sg0) raw-normalised (sg0zmuv),
		%(sg1) normalised-smoothed 1 and
		%(sg1) normalised-smoothed 2)
		%and with one sensor attached to the participant (HS01)
		%and other sensor attached to the robot (RS01).
	Code and data to reproduce the figure is available in \cite{srep2021}.
        }
    \label{fig-p02-V-w250}
\end{figure}
%---------------------------------(FIGURE)------------------------------------

\newpage
%---------------------------------FIGURE)-------------------------------------
\begin{figure}[ht!]
\centering
\includegraphics{figures/rqa/output/epsilons/rqa-epsilonsp02w500Horizontal}
    	\caption{
	{\bf RQA-Entr for participant 02 performing horizontal movements for a window size of 500 samples.}
		%RQA-Entr surface plots are for participant $p02$
		%for horizontal and vertical arm movements in normal
		%and faster velocity (HN, HF, VN, VF)
		%with the normalised GyroZ or GyroY axis
		%((sg0) raw-normalised (sg0zmuv),
		%(sg1) normalised-smoothed 1 and
		%(sg1) normalised-smoothed 2)
		%and with one sensor attached to the participant (HS01)
		%and other sensor attached to the robot (RS01).
	Code and data to reproduce the figure is available in \cite{srep2021}.
        }
    \label{fig-p02-H-w500}
\end{figure}
%---------------------------------(FIGURE)------------------------------------
%---------------------------------FIGURE)-------------------------------------
\begin{figure}[hb!]
\centering
\includegraphics{figures/rqa/output/epsilons/rqa-epsilonsp02w500Vertical}
    	\caption{
	{\bf RQA-Entr for participant 02 performing vertical movements for a window size of 500 samples.}
		%RQA-Entr surface plots are for participant $p02$
		%for horizontal and vertical arm movements in normal
		%and faster velocity (HN, HF, VN, VF)
		%with the normalised GyroZ or GyroY axis
		%((sg0) raw-normalised (sg0zmuv),
		%(sg1) normalised-smoothed 1 and
		%(sg1) normalised-smoothed 2)
		%and with one sensor attached to the participant (HS01)
		%and other sensor attached to the robot (RS01).
	Code and data to reproduce the figure is available in \cite{srep2021}.
        }
    \label{fig-p02-V-w500}
\end{figure}
%---------------------------------(FIGURE)------------------------------------

\newpage
%---------------------------------FIGURE)-------------------------------------
\begin{figure}[ht!]
\centering
\includegraphics{figures/rqa/output/epsilons/rqa-epsilonsp02w750Horizontal}
    	\caption{
	{\bf RQA-Entr for participant 02 performing horizontal movements for a window size of 750 samples.}
		%RQA-Entr surface plots are for participant $p02$
		%for horizontal and vertical arm movements in normal
		%and faster velocity (HN, HF, VN, VF)
		%with the normalised GyroZ or GyroY axis
		%((sg0) raw-normalised (sg0zmuv),
		%(sg1) normalised-smoothed 1 and
		%(sg1) normalised-smoothed 2)
		%and with one sensor attached to the participant (HS01)
		%and other sensor attached to the robot (RS01).
	Code and data to reproduce the figure is available in \cite{srep2021}.
        }
    \label{fig-p02-H-w750}
\end{figure}
%---------------------------------(FIGURE)------------------------------------
%---------------------------------FIGURE)-------------------------------------
\begin{figure}[hb!]
\centering
\includegraphics{figures/rqa/output/epsilons/rqa-epsilonsp02w750Vertical}
    	\caption{
	{\bf RQA-Entr for participant 02 performing vertical movements for a window size of 750 samples.}
		%RQA-Entr surface plots are for participant $p02$
		%for horizontal and vertical arm movements in normal
		%and faster velocity (HN, HF, VN, VF)
		%with the normalised GyroZ or GyroY axis
		%((sg0) raw-normalised (sg0zmuv),
		%(sg1) normalised-smoothed 1 and
		%(sg1) normalised-smoothed 2)
		%and with one sensor attached to the participant (HS01)
		%and other sensor attached to the robot (RS01).
	Code and data to reproduce the figure is available in \cite{srep2021}.
        }
    \label{fig-p02-V-w750}
\end{figure}
%---------------------------------(FIGURE)------------------------------------
